\section{Local Feature Detection}

\subsection*{Desired Properties of Local Features}
1. \textbf{Repeatability}: Detectable across images despite transformations.\\
2. \textbf{Saliency}: Be distinct. \\
3. \textbf{Efficiency}: Lighter than total pixels. \\
4. \textbf{Locality}: Cover small, clutter-resistant regions.


\subsection*{Corners as Interest Points}
1. \textbf{Flat Region}: No intensity change in any direction. \\
2. \textbf{Edge}: No change along the edge direction. \\
3. \textbf{Corner}: Large change in all directions.
\subsection*{Harris Corner Detector}
Invariant to rotation, not scale\\
1. \textbf{Compute $M$} for each image window:
    \[
    M = 
    \begin{bmatrix}
    \sum I_x^2 & \sum I_x I_y \\
    \sum I_x I_y & \sum I_y^2
    \end{bmatrix}
    \] \\
2. \textbf{Corner Response Function}:
    \[
    R = \det(M) - \alpha \cdot (\text{trace}(M))^2
    \] \\
3. \textbf{Thresholding}: Retain points with large $R$ values. \\
4. \textbf{Non-Maximum Suppression}: Keep local maxima to avoid redundant corners.

\subsection*{Blob Detection and Scale Selection}
1. Scale-invariant but not rotation.\\
2. \textbf{Laplacian of Gaussian (LoG)}:
    \[
    \nabla^2 G = \frac{\partial^2 G}{\partial x^2} + \frac{\partial^2 G}{\partial y^2}
    \]
3. \textbf{Characteristic Scale}: Scale at which the LoG response is maximized.

\subsection*{Feature Matching}
1. Extract keypoint features.\\
2. Compute potential matches between images.\\
3. Hypothesize transformation $T$ to align related matches.\\
4. Verify transformation by checking for consistency across matches.

